Native advertising as a content marketing strategy

### 2024-09-17 analysis/paper/paper.Rmd
weiter

---
title: Native advertising as a content marketing strategy
author:
  - name: Davor Trbusic
    email: davor.trbusic@unicath.hr
    affiliation: Croatian Catholic University
    correspondingauthor: true
    footnote: 1
  - name: Drazen Males
    email: dmales@fhs.hr
    affiliation: Faculty of Croatian Studies
  - name: Luka Sikic
    email: luka.sikic@unicath.hr
    affiliation: Croatian Catholic University
    footnote: 2
address:
  - code: Croatian Catholic University
    organization: Croatian Catholic University
    addressline: Ilica 242
    city: Zagreb
    state: 
    postcode: 10000
    country: Croatia
  - code: Faculty of Croatian Studies
    organization: Faculty of Croatian Studies
    addressline: Borongajska cesta 83d
    postcode: 10000
    city: Zagreb
    country: Croatia
footnote:
  - code: 1
    text: "This is the corresponding author."
  - code: 2
    text: "Co-author of the study."
abstract: |
  Purpose – The objective of this study is to determine the content characteristics of native advertisements (as one of the content marketing strategies) on the most-read Croatian internet portals. Specifically, the study aims to identify key characteristics of headlines and content, and their relationship with audience reach. Design/Methodology/Approach – A machine-based pre-analysis that included all posts on Croatian internet portals during the observed period resulted in defining a final sample of 543 native ads on the most influential online media in the Croatian digital space, based on visitor criteria. The research on a sample of 543 native advertisements was conducted using content analysis methodology. Findings and implications – The findings reveal that nearly 80% of headlines contain at least one clickbait characteristic, with the style of uncertainty being the most frequently employed and effective. Half of the ads did not include any statements or sources, with the most common sources being individuals from the organization or company. The effectiveness of different source types varies across industries, with multiple sources proving most effective in sectors like non-alcoholic beverages and construction, while direct user testimonials are more impactful in technology and finance. Limitations – Due to the focus on native advertisements published in Croatian media space, results may not fully reflect the global native advertising landscape. The selected sample was based on the most-read portals according to visitor numbers, which may not represent niche platforms or smaller but influential digital spaces. Lastly, the time frame for data collection might not capture trends or changes in native advertising strategies over time, limiting the ability to generalize the findings beyond the observed period. Originality – The research underscores the significant role of clickbait headlines, visual content, and source credibility in the success of native advertising as a content marketing strategy.

keywords: 
  - native advertising
  - content analysis
  - headline characteristics
journal: "An awesome journal"
date: "`r Sys.Date()`"
linenumbers: false
numbersections: true
bibliography: refs.bib
output: 
  html_document:
    toc: true
    toc_float: true
    number_sections: true
    df_print: kable

---

>>>>

---
title: "Native advertising as a content marketing strategy"
author:
- name: Davor Trbusic
  email: davor.trbusic@unicath.hr
  affiliation: Croatian Catholic University
  correspondingauthor: yes
  footnote: 1
- name: Drazen Males
  email: dmales@fhs.hr
  affiliation: Faculty of Croatian Studies
- name: Luka Sikic
  email: luka.sikic@unicath.hr
  affiliation: Croatian Catholic University
  footnote: 2
date: "`r Sys.Date()`"
output:
  word_document:
    toc: yes
  html_document:
    toc: yes
    toc_float: yes
    number_sections: yes
    df_print: kable
abstract: "Purpose – The objective of this study is to determine the content characteristics
  of native advertisements (as one of the content marketing strategies) on the most-read
  Croatian internet portals. Specifically, the study aims to identify key characteristics
  of headlines and content, and their relationship with audience reach. Design/Methodology/Approach
  – A machine-based pre-analysis that included all posts on Croatian internet portals
  during the observed period resulted in defining a final sample of 543 native ads
  on the most influential online media in the Croatian digital space, based on visitor
  criteria. The research on a sample of 543 native advertisements was conducted using
  content analysis methodology. Findings and implications – The findings reveal that
  nearly 80% of headlines contain at least one clickbait characteristic, with the
  style of uncertainty being the most frequently employed and effective. Half of the
  ads did not include any statements or sources, with the most common sources being
  individuals from the organization or company. The effectiveness of different source
  types varies across industries, with multiple sources proving most effective in
  sectors like non-alcoholic beverages and construction, while direct user testimonials
  are more impactful in technology and finance. Limitations – Due to the focus on
  native advertisements published in Croatian media space, results may not fully reflect
  the global native advertising landscape. The selected sample was based on the most-read
  portals according to visitor numbers, which may not represent niche platforms or
  smaller but influential digital spaces. Lastly, the time frame for data collection
  might not capture trends or changes in native advertising strategies over time,
  limiting the ability to generalize the findings beyond the observed period. Originality
  – The research underscores the significant role of clickbait headlines, visual content,
  and source credibility in the success of native advertising as a content marketing
  strategy.\n"
keywords:
- native advertising
- content analysis
- headline characteristics
journal: An awesome journal
address:
- code: Croatian Catholic University
  organization: Croatian Catholic University
  addressline: Ilica 242
  city: Zagreb
  state: null
  postcode: 10000
  country: Croatia
- code: Faculty of Croatian Studies
  organization: Faculty of Croatian Studies
  addressline: Borongajska cesta 83d
  postcode: 10000
  city: Zagreb
  country: Croatia
linenumbers: no
numbersections: yes
always_allow_html: true
bibliography: refs.bib
footnote:
- code: 1
  text: This is the corresponding author.
- code: 2
  text: "Co-author of the study."
---
